ODGI: understanding pangenome graphs

### 2021-10-22 manuscript/main.tex
Added missing output 4.2 commands listed in intro of 4.

@@

\textit{odgi degree/position/depth/untangle/tips} all can output the BED format~\citep{Quinlan_2010}.

@@

ODGI provides common operation on on standard pangenomic file formats, such as GFA. ODGI aims to be a reference implementation for many pangenome related operations. In the near future we aim to improve RDF support for annotation in the in-memory graph\cite{Yokoyama2020}, for example, and allow for federated queries on the pangenome, and FAIR data sharing.

>>>>

\textit{odgi matrix} derives the pangenome matrix and writes the graph topology in sparse matrix formats.

\textit{odgi paths} allows the investigation of paths of a given variation graph. It can calculate overlap statistics of groupings of paths and extracts FASTA.

\textit{odgi flatten} projects the graph sequence and paths into FASTA and BED.

@@

\textit{odgi degree/position/depth/untangle/tips} all can output the BED format.

@@

ODGI provides common operation on on standard pangenomic file formats, such as GFA. ODGI aims to be a reference implementation for many pangenome related operations. In the near future we aim to improve RDF support for annotation in the in-memory graph~\citep{Yokoyama2020}, for example, and allow for federated queries on the pangenome, and FAIR data sharing.
